### 2018-04-10 latex/icpp18/introduction.tex
oguz comments

NMF is widely used in data mining and machine learning as a dimension reduction and factor analysis method.
It is a natural fit for many real world problems as the non-negativity is inherent in many representations of real-world data and
the resulting low rank factors are expected to have a natural interpretation. The applications of NMF range from text mining \cite{pauca2004text},  computer vision \cite{hoyer2004non}, and bioinformatics \cite{kim2007sparse} to blind source separation  \cite{cichocki2009nonnegative}, unsupervised clustering \cite{kuang2012symmetric,kuang2013symnmf}  and many other areas.
In most real-world applications $m$ and $n$ are on the order of millions or more while $k$ is much smaller, on the order of tens to thousands.
Furthermore, data sets from these applications are often quite sparse and have highly irregular nonzero patterns.

>>>>

NMF is widely used in data mining and machine learning as a dimension reduction and factor analysis method.
It is a natural fit for many real world problems as the non-negativity is inherent in many representations of real-world data and
the resulting low rank factors are expected to have a natural interpretation. The applications of NMF range from text mining \cite{pauca2004text},  computer vision \cite{hoyer2004non}, and bioinformatics \cite{kim2007sparse} to blind source separation  \cite{cichocki2009nonnegative}, unsupervised clustering \cite{kuang2012symmetric,kuang2013symnmf}  and many other areas.
In most real-world applications $m$ and $n$ are on the order of millions or more while $k$ is much smaller, on the order of tens to thousands. Furthermore, data sets from these applications are often quite sparse and have highly irregular nonzero patterns.
We would like to highlight that ``Non-negative'' Matrix Factorization is NOT matrix factorization in collaborative filtering for recommender systems for which many implementations exist.
The collaborative filtering problem is different than NMF -- the focus of our paper -- because it interprets the ``{\em zero}'' entries of the input matrix as missing data, while the NMF problem is defined for a completely known input matrix and does not handle missing values.
This leads to different optimization problems, algorithms, and computational steps.

%However, we would like to clarify that collaborative filtering in recommender systems using matrix factorization is a different problem than NMF: in the case of collaborative filtering, non-nonzeros in the matrix are considered to be missing entries, while in the case of NMF, non-nonzeros in the matrix correspond to true zero values.
